### 2012-07-24 docs/mg/mg.tex
define mgfigpath
add notes about the different MG solves

\maestro\ uses multigrid to enforce the velocity constraint through
projections at the half-time (the MAC projection) and end of the time
step.  Two multigrid solvers are provided by \boxlib---one for
cell-centered data and one for node-centered (nodal) data.

\begin{figure}[t]
\centering
\includegraphics[width=5.5in]{MAC_mg2}
\caption{\label{fig:mg:MAC} Data centerings for the MAC projection}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=5.5in]{HG_mg2}
\caption{\label{fig:mg:HG} Data centerings for the HG projection}
\end{figure}

>>>>

\maestro\ uses multigrid to enforce the velocity constraint through
projections at the half-time (the MAC projection) and end of the time
step (the HG projection).  Two multigrid solvers are provided by
\boxlib---one for cell-centered data and one for node-centered (nodal)
data.  Both of these are used in \maestro.

\begin{figure}[t]
\centering
\includegraphics[width=5.5in]{\mgfigpath/MAC_mg2}
\caption{\label{fig:mg:MAC} Data centerings for the MAC projection}
\end{figure}

The MAC projection operates on the advective velocities predicted at
the cell-interfaces at the half-time.  The edge-centered velocities
are shown in Figure~\ref{fig:mg:MAC}.  If we consider purely
incompressible flow, the projection appears as:
\begin{equation}
D G \phi = D U
\end{equation}
where $D$ is the divergence operator and $G$ is the gradient operator.
In this discretization, $\phi$ is cell-centered (see
Figure~\ref{fig:mg:MAC}).  The remaining quantities are discretized as:
\begin{itemize}
\item $DU$ is cell-centered, 
  \begin{equation}
  (DU)_{i,j} = \frac{u_{i+1/2,j} - u_{i-1/2,j}}{\Delta x} + 
               \frac{v_{i,j+1/2} - v_{i,j-1/2}}{\Delta y}
  \end{equation}

\item $G\phi$ is edge-centered, on the MAC grid, as shown in
  Figure~\ref{fig:mg:MAC}.

\item $DG\phi$ is cell-centered, also shown in Figure~\ref{fig:mg:MAC},
  computed from $G\phi$ using the same differencing as $DU$.

\begin{figure}[t]
\centering
\includegraphics[width=5.5in]{\mgfigpath/HG_mg2}
\caption{\label{fig:mg:HG} Data centerings for the HG projection}
\end{figure}

The HG projection projects the cell-centered velocities at the end of
the timestep.  Here, $\phi$ is node-centered.  Figure~\ref{fig:mg:HG}
shows the locations of the various quantities involved in the HG
projection.  Again considering simple incompressible flow, we now
solve:
\begin{equation}
L \phi = D U
\end{equation}
where $L$ is a discretization of the Laplacian operator.  In this
sense, the HG projection is an {\em approximate projection}, that is,
$L \neq DG$ (in discretized form).  The various operations have the
following centerings:
\begin{itemize}

\item $DU$ is node-centered.  This is computed as:
  \begin{equation}
  (DU)_{i-1/2,j-1/2} = \frac{\frac{1}{2} (u_{i,j} + u_{i,j-1}) -
                             \frac{1}{2} (u_{i-1,j} + u_{i-1,j-1})}{\Delta x} +
                       \frac{\frac{1}{2} (v_{i,j} + v_{i-1,j}) -
                             \frac{1}{2} (v_{i,j-1} + v_{i-1,j-1})}{\Delta y} 
  \end{equation}

\item $G\phi$ is cell-centered, as shown in Figure~\ref{fig:mg:HG}.

\item $L\phi$ is node-centered.  This is a direct discretization of 
the Laplacian operator.  By default, \maestro\ uses a dense stencil
(9-points in 2-d, 27-points in 3-d).  Alternately, a {\em cross}
stencil can be used (by setting {\tt hg\_dense\_stencil = F}).  This
uses 5-points in 2-d, 7-points in 3-d.
